Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-12-18 latex/toms/experiments.tex
mouse plots completed

%%%%%%%%%%%%%%%%%
%Strong Scaling Realworld Low Rank
%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth, height=3in]{data/plots/ssrw_tinyimagenet_no16.pdf}
\caption {Strong Scaling on Realworld Tiny Imagenet Dataset on 32, 64, 128, 256, 512 and 1024 nodes in Titan. The algorithms alg=0,1,2,4,5,6 are \MU, \HALS, \BPP, \ADMM, \Nestrov, \CPALS\ respectively.}
\label{fig:synstrongscaling}
\end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%%
%Strong Scaling Realworld Low Rank
%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth, height=3in]{data/plots/ssrw_tinyimagenet_breakdown.pdf}
\caption {Strong Scaling on Realworld Tiny Imagenet Dataset on 32, 64, 128, 256, 512 and 1024 nodes in Titan. The algorithms alg=0,1,2,4,5,6 are \MU, \HALS, \BPP, \ADMM, \Nestrov, \CPALS\ respectively.}
\label{fig:synstrongscaling}
\end{figure}

@@

%%%%%%%%%%%%%%%%%
%Mouse Data
%%%%%%%%%%%%%%%%%
\begin{figure}
	\subfloat[Low rank $k=64$ \label{fig:accuracyrwk64}]{
		\includegraphics[width=0.45\textwidth, height=2in]{data/plots/accuracymouse64.pdf}
	}
	\subfloat[Low rank $k=96$ \label{fig:accuracyrwk96}]{
		\includegraphics[width=0.45\textwidth, height=2in]{data/plots/accuracymouse96.pdf}
	}
	\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Realworld Low Rank Tensor of size $1040\times1392\times69\times25$ on 64 Titan Nodes as $8\times8\times1\times1$ Processor Grid.}
	\label{fig:convergencemouse}
\end{figure}

\begin{figure}
   \includegraphics[width=0.45\textwidth, height=2in]{data/plots/lucmouse64.pdf}
	\caption{LUC comparison of \MU, \HALS, \BPP, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size $1040\times1392\times69\times25$ on 64 Titan nodes as $8\times8\times1\times1$ Processor Grid}
	\label{fig:luccompmouse}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth, height=3in]{data/plots/ssrw_mouse.pdf}
	\caption {Strong Scaling on Realworld Mouse MRI Dataset on 32, 64, 128, 256, 512 and 1024 nodes in Titan. The algorithms alg=0,1,2,4,5,6 are \MU, \HALS, \BPP, \ADMM, \Nestrov, \CPALS\ respectively.}
	\label{fig:synstrongscaling}
\end{figure}
